TBD

### 2024-04-01 doc/paper.tex
Focus on a smaller set of benchmarks

\begin{description}
  \item[\texttt{Ref}:] during smoothing, when unit clauses (a.k.a.\ variables)
        are propagated in the opposite direction of the FCG arcs (i.e.,
        `upwards'), when visiting a \texttt{Ref} node, these clauses are
        translated using the domain map of the \texttt{Ref} node. For example,
        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
        mentions $\Delta$, then replace it by $\Delta'$.
  \item[Constraint removal:] do reverse constraint removal. Assuming that
        domain $\Delta$ with constraints $X \ne c$ (for some constant
        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
        $\forall X \in \Delta'\text{. }\phi(X)$ with
        $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
  \item[Domain recursion:] we merge $P(c)$ and $\forall X \in \Delta\text{.
        }X \ne c \Rightarrow P(X)$ into $\forall X \in \Delta\text{. }P(X)$.
        NOTE: the clauses may have other constraints, variables, etc. I could
        describe this more formally.
\end{description}

@@

\begin{description}
  \item[\texttt{Ref}:] nothing.
  \item[Constraint removal:] nothing.
  \item[Domain recursion:] Smoothing for domain recursion now works the same way
        as smoothing for disjunction: both sides must have the same atoms EXCEPT
        the `base case' side need not include unit clauses that mention the
        constant introduced by this domain recursion node or its domain (since
        this branch assumes that this domain is empty). NOTE: As a consequence,
        almost all of \cref{sec:simplifying} is now outdated because smoothing
        makes the ``tautology insertion'' unnecessary.
\end{description}

>>>>

\begin{description}
  \item[\texttt{Ref}.] During smoothing, when unit clauses (a.k.a.\ variables)
        are propagated in the opposite direction of the FCG arcs (i.e.,
        `upwards'), when visiting a \texttt{Ref} node, these clauses are
        translated using the domain map of the \texttt{Ref} node. For example,
        if the domain map include $\Delta \mapsto \Delta'$, and the unit clause
        mentions $\Delta$, then replace it by $\Delta'$.
  \item[Constraint removal.] Do reverse constraint removal. Assuming that
        domain $\Delta$ with constraints $X \ne c$ (for some constant
        $c \in \Delta$) were replaced with domain $\Delta'$, replace each
        $\forall X \in \Delta'\text{. }\phi(X)$ with
        $\forall X \in \Delta\text{. }X \ne c \Rightarrow \phi(X)$.
  \item[Domain recursion.] Suppose the domain recursion node introduces constant
        $x \in \Delta$. For each unit clause received from the child node,
        replace each occurrence of $\phi(x)$ or $\forall X \in \Delta\text{.
        } X \ne x \Rightarrow \phi(X)$ with $\forall X \in \Delta\text{.
        }\phi(X)$. This can be seen as a claim about what ground atoms the
        domain recursion node \emph{should} cover (or a temporary assumption).
        If the relevant subgraph indeed covers those ground atoms, Stage~2 will
        do nothing. Otherwise, smoothing nodes will be added below the domain
        recursion node to cover the difference between what was propagated from
        the domain recursion node and what was received from the child node.
\end{description}
\todo[inline]{Add examples of both cases, with figures.}

@@

% TODO
% \item Whenever the set of unit clauses received from the child node contains two
% formulas $\phi(x)$ and $\forall X \in \Delta\text{.
% } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference between the two
% formulas is that one has the constant $x$ whereas the other one has a variable
% $X \ne x$), merge them into $\forall X \in \Delta\text{. }\phi(X)$.

\begin{description}
  \item[\texttt{Ref}:] nothing.
  \item[Constraint removal:] nothing.
  \item[Domain recursion:]
        \begin{enumerate}
          \item Whenever the set of unit clauses of the child node contains two
                formulas $\phi(x)$ and $\forall X \in \Delta\text{.
                } X \ne x \Rightarrow \phi(X)$ (i.e., the only difference
                between the two formulas is that one has the constant $x$
                whereas the other one has a variable $X \ne x$), merge them into
                $\forall X \in \Delta\text{. }\phi(X)$.
          \item Add smoothing nodes below the domain recursion node for the
                difference between the unit clauses assigned to the domain
                recursion node during Stage 1 and the unit clauses of the child
                node post-processed by the step above. For example, if the child
                node `covers' only $p(x)$, then Stage 1 assigns
                $\forall X \in \Delta\text{. }p(X)$ to the domain recursion
                node. The smoothing node below the domain recursion node then
                has the clause $\forall X \in \Delta\text{.
                } X \ne x \Rightarrow p(X)$.
        \end{enumerate}
\end{description}

\todo[inline]{Can I formally define what is meant by `difference'?}
